Choosing climate forcing for numerical simulations of the Cordilleran ice sheet

### 2013-02-19 sections/model.tex
Fancier todo notes

Monthly temperatures and precipitation rates are converted to surface accumulation and ablation using a temperature-index (positive degree-day) model. Accumulation is computed as the amount of precipitation that falls when temperature is below freezing.\askconstantine{Is this true? What is the current threshold in stable 0.5?} Ablation is computed from the number of positive degree-days, defined as the integrand of temperatures above 0\,\degree\,C in one year. Positive degree-days are computed by the \citet{calov-greve-2011} formula to account for day-to-day variability unrepresented in the monthly climate forcing. The ablation model use different degree-day factors for snow and ice and accounts for refreezing. Complete description of the ablation model is available in PISM documentation \citep[{\url{http://www.pism-docs.org}},][]{web:pism} and model parameters are explicited in table~\ref{tab:pdd}.

\todo[inline]{
	\textbf{Include the \citet{calov-greve-2011} integrand formula?}

@@

A positive degree-day model is a very crude approximation of physical processes occurring at a glacier's surface. Yet we believe that it captures regional patterns of accumulation and ablation resonable enough for our study if accurate climate data is used, as we will show further.\todo{Is this paragraph really needed?}

@@

\todo[inline]{
	\textbf{Include SSA+SIA \citet{bueler-brown-2009} formula?}

@@

The glacier bed topography responds to the ice load following a regional isostasy model with flexure and relaxation \citep{lingle-clark-1985}\todo{check ref.}.

>>>>

Monthly temperatures and precipitation rates are converted to surface accumulation and ablation using a temperature-index (positive degree-day) model. Accumulation is computed as the amount of precipitation that falls when temperature is below freezing.\ask{Is this true? What is the current threshold in stable 0.5?} Ablation is computed from the number of positive degree-days, defined as the integrand of temperatures above 0\,\degree\,C in one year. Positive degree-days are computed by the \citet{calov-greve-2011} formula to account for day-to-day variability unrepresented in the monthly climate forcing. The ablation model use different degree-day factors for snow and ice and accounts for refreezing. Complete description of the ablation model is available in PISM documentation \citep[{\url{http://www.pism-docs.org}},][]{web:pism} and model parameters are explicited in table~\ref{tab:pdd}.

\ask[inline]{\emph{Should I include the \citet{calov-greve-2011} integrand formula?}

@@

A positive degree-day model is a very crude approximation of physical processes occurring at a glacier's surface. Yet we believe that it captures regional patterns of accumulation and ablation resonable enough for our study if accurate climate data is used, as we will show further.\ask{Is this paragraph really needed?}

@@

\ask[inline]{\emph{Should I include the SSA+SIA \citet{bueler-brown-2009} formula?}

@@

The glacier bed topography responds to the ice load following a regional isostasy model with flexure and relaxation \citep{lingle-clark-1985}\todo{Check \citet{lingle-clark-1985}}.
